Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-06 edubots_surveys.Rnw
Fix grammar and typos - intro p3

\textcolor{blue}{\textit{Chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user. 
Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their 
engagement and participation in the subjects \cite{agarwal2020}. Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher, 
or asking questions in front of the class. This situation normally conducts to a silence of the student and a later contact with the teacher by e-mail, which, in turn, will mean a workload for the teacher, that could be very 
significant given the existing disproportion between number of students per each teacher.  
}
Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding.

>>>>

\textcolor{blue}{\textit{Chatbots} are autonomous agents that are able to communicate and interact in a human-like way \cite{Gong2008}, answering question and even posing their own ones to the user. 
Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
Within the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
\textit{personalized learning}, i.e. they adapt themselves to students' self-pace learning and provide online tutoring. Personalized learning has been proved to be very effective increasing students course engagement and participation \cite{agarwal2020}. Moreover, chatbots also reduce students' stress \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teachers, 
or asking questions in front of the class. This situation usually results in a later contact with the teacher by e-mail, which in turn, will mean a workload for the teacher that could be very 
significant given the disproportionate ratio of number of students to teachers.  
}
Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning
experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot will allow teachers to spend more time on  other topics that students struggle with.
